\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-04-06 Drafts and notes/Notes/old_draft_2.tex
Major change

\section{Rate of convergence via the doubling variables method}
\noindent The main result is the following Theorem.

\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(\frac{3}{2},2\right)$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ satisfying $f\geq 0$ in $\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that

@@

@@

@@

    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1} \qquad\text{where}\qquad \alpha = \frac{2-p}{p-1} \in (0,1) \quad\text{and}\quad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.

@@

    G = \left[\left(1+\frac{K_1\delta_0}{\alpha+1}\right)^{\alpha+1} - 1\right]C_\alpha 
then for $\eta = G\varepsilon^{\alpha+1}$, we have 
    \mathcal{W}(x) = \frac{(C_\alpha+G)\varepsilon}{d(x)^\alpha} + \frac{M_\varepsilon}{\lambda}, \qquad x\in \Omega \qquad\text{where}\qquad M_\varepsilon = \sup_{\Omega} f + C\varepsilon^{\alpha+2}.
is a supersolution of \eqref{eq:PDEeps} in $\Omega$. Here $C$ depends only on $K,\alpha,\delta_0$. We therefore can assume $M_\varepsilon\leq \lambda M$ independent of $\varepsilon>0$. Let 

@@

then 

@@

    u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \leq M \qquad\text{for all}\; x\in \Omega.

@@

    u^\varepsilon(x) - (1+\delta) \frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M - \delta\frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta G_\alpha\varepsilon^{\alpha+1}}{M}\right)^{\frac{1}{\alpha}}.

@@

    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.

@@

        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.

@@

          & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(z) - u(z) - \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.

@@

        \delta\left(\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) \leq \left(u^\varepsilon(x) - \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) + \left(1+2\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.

@@

>>>>

\section{Rate of convergence via the doubling variables method}

\begin{thm}\label{thm:rate_doubling0} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $H(x,\xi) = |\xi|^p - f(x)$ where $p\in\left(1,2\right)$ and $f\equiv 0$ in $\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}, then there exists a constant $C$ independent of $\varepsilon$ such that

@@

\color{blue}
This assumption $f\equiv 0$ effectively renders our theorem useless, since it is radical, it can be reduced to a one dimensional problem (probably uninteresting result).
\color{black}

@@

    \sup_{x\in \overline{\Omega}} \left(\left| u(x)\right| + \left|Du(x)\right|\right)  \leq C_0.

@@

    \lim_{d(x)\to 0^+} u^\varepsilon(x)d(x)^\alpha = C_\alpha \varepsilon^{\alpha+1} \qquad\text{where}\qquad \alpha = \frac{2-p}{p-1} \quad\text{and}\quad C_\alpha := \frac{1}{\alpha}(\alpha+1)^{\alpha+1}.

@@

@@

then by Lemma \ref{lem:subsln}

@@

    u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} \leq M_\alpha\varepsilon^{\alpha+2} \qquad\text{for all}\; x\in \Omega.

@@

    u^\varepsilon(x) - (1+\delta) \frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}} \leq  M_\alpha\varepsilon^{\alpha+2} - \delta\frac{G_\alpha \varepsilon^{\alpha+1}}{d(x)^{\alpha}}\leq 0 \qquad\text{if}\qquad d(x)< \left(\frac{\delta G_\alpha\varepsilon^{\alpha+1}}{M}\right)^{\frac{1}{\alpha}}.

@@

    \Phi(x,y) =  u^\varepsilon(x) - u(y) - \frac{C_0|x-y|^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.

@@

        & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(x_\sigma) - u(x_\sigma) - \frac{C_0|x_\sigma-x_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}.

@@

          & u^\varepsilon(x_\sigma) - u(y_\sigma) - \frac{C_0|x_\sigma-y_\sigma |^2}{\sigma}- \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}} \\
        & \qquad\qquad\qquad\qquad \geq u^\varepsilon(z) - u(z) - \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.

@@

        \delta\left(\frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) &\leq \left(u^\varepsilon(x) - \frac{G_\alpha\varepsilon^{\alpha+1}}{d(x_\sigma)^{\alpha}}\right) + \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}\\
        &\leq M_\alpha\varepsilon^{\alpha+2} + \left(1+\delta\right)\frac{G_\alpha\varepsilon^{\alpha+1}}{\theta^{\alpha}}.

@@

    Therefore, using $1+\delta\leq 2$
        \frac{1}{d(x_\sigma)^\alpha}\leq \left(\frac{G_\alpha}{M_\alpha}\right) \frac{\varepsilon}{\delta} + \frac{2G_\alpha}{\delta\theta^\alpha}  .
    Choose $\delta = \varepsilon^\beta$ for $0<\beta<1$ then 
        \frac{1}{d(x_\sigma)^\alpha} \leq \frac{C}{\delta\theta^\alpha} \qquad\Longrightarrow\qquad    d(x_\sigma)\geq C\theta \delta^{\frac{1}{\alpha}} = C\theta\varepsilon^{\frac{\beta}{\alpha}}.
